Graphical Tests for Power Comparison of Competing Designs

### 2012-03-29 experiment-two.tex
images for second experiment
second experiment

\subsection{Comparing Distributions}

\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -2.00 & 0.38 & -5.29 & 0.00 \\ 
  test\_paramdensity & -0.17 & 0.53 & -0.32 & 0.75 \\ 
  test\_paramdotplot & -0.72 & 0.52 & -1.39 & 0.17 \\ 
  test\_paramhistogram & -0.30 & 0.53 & -0.58 & 0.56 \\ 
  d & 1.77 & 0.34 & 5.19 & 0.00 \\ 
  n1 & 0.02 & 0.00 & 9.80 & 0.00 \\ 
  I(n1/n2) & -0.31 & 0.11 & -2.93 & 0.00 \\ 
  test\_paramdensity:d & -0.67 & 0.47 & -1.42 & 0.15 \\ 
  test\_paramdotplot:d & 0.05 & 0.46 & 0.11 & 0.91 \\ 
  test\_paramhistogram:d & -0.27 & 0.48 & -0.56 & 0.57 \\ 
  test\_paramdensity:n1 & -0.00 & 0.00 & -0.40 & 0.69 \\ 
  test\_paramdotplot:n1 & -0.01 & 0.00 & -3.06 & 0.00 \\ 
  test\_paramhistogram:n1 & -0.01 & 0.00 & -2.67 & 0.01 \\ 
  test\_paramdensity:I(n1/n2) & 0.06 & 0.15 & 0.42 & 0.68 \\ 
  test\_paramdotplot:I(n1/n2) & 0.27 & 0.15 & 1.81 & 0.07 \\ 
  test\_paramhistogram:I(n1/n2) & 0.10 & 0.15 & 0.65 & 0.52 \\ 
   \hline
\end{tabular}
\end{center}
\end{table}

>>>>

% !TEX root = comparison.tex
\subsection{Comparing Distributions}

\begin{figure*} [hbtp]
   \centering
   \includegraphics[width=0.245\textwidth]{hist-conc} 
   \includegraphics[width=0.245 \textwidth]{boxplot-conc} 
   \includegraphics[width=0.245 \textwidth]{density-conc} 
   \includegraphics[width=0.245 \textwidth]{dotplot-conc} 
   \caption{Overview of all four competing designs for displaying differences in distributions.}
   \label{fig:expii}
\end{figure*}

\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -2.00 & 0.38 & -5.29 & 0.00 \\ 
  density & -0.29 & 0.53 & -0.55 & 0.58 \\ 
  dotplot & -0.72 & 0.52 & -1.39 & 0.17 \\ 
  histogram & -0.29 & 0.53 & -0.54 & 0.59 \\ 
  d & 1.78 & 0.34 & 5.22 & 0.00 \\ 
  n1 & 0.02 & 0.00 & 9.77 & 0.00 \\ 
  I(n1/n2) & -0.31 & 0.11 & -2.94 & 0.00 \\ 
  density:d & -0.61 & 0.47 & -1.29 & 0.20 \\ 
  dotplot:d & 0.04 & 0.46 & 0.08 & 0.94 \\ 
  histogram:d & -0.29 & 0.48 & -0.60 & 0.55 \\ 
  density:n1 & -0.00 & 0.00 & -0.40 & 0.69 \\ 
  dotplot:n1 & -0.01 & 0.00 & -3.04 & 0.00 \\ 
  histogram:n1 & -0.01 & 0.00 & -2.67 & 0.01 \\ 
  density:I(n1/n2) & 0.09 & 0.15 & 0.59 & 0.55 \\ 
  dotplot:I(n1/n2) & 0.27 & 0.15 & 1.81 & 0.07 \\ 
  histogram:I(n1/n2) & 0.09 & 0.15 & 0.62 & 0.53 \\ 
   \hline
\end{tabular}
\end{center}
\caption{correctness}
\end{table}

\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std..Error & t.value & pval \\ 
  \hline
(Intercept) & 3.85 & 0.09 & 42.21 & 0.00 \\ 
  density & 0.01 & 0.12 & 0.07 & 0.94 \\ 
  dotplot & 0.03 & 0.12 & 0.26 & 0.80 \\ 
  histogram & 0.23 & 0.12 & 1.97 & 0.05 \\ 
  d & -0.23 & 0.08 & -3.02 & 0.00 \\ 
  n1 & 0.00 & 0.00 & 1.74 & 0.08 \\ 
  I(n1/n2) & -0.04 & 0.02 & -1.48 & 0.14 \\ 
  density:d & 0.11 & 0.11 & 1.02 & 0.31 \\ 
  dotplot:d & 0.20 & 0.11 & 1.86 & 0.06 \\ 
  histogram:d & -0.01 & 0.11 & -0.09 & 0.93 \\ 
  density:n1 & -0.00 & 0.00 & -2.15 & 0.03 \\ 
  dotplot:n1 & -0.00 & 0.00 & -2.87 & 0.00 \\ 
  histogram:n1 & -0.00 & 0.00 & -0.93 & 0.35 \\ 
  density:I(n1/n2) & 0.04 & 0.03 & 1.18 & 0.24 \\ 
  dotplot:I(n1/n2) & 0.02 & 0.03 & 0.65 & 0.52 \\ 
  histogram:I(n1/n2) & 0.00 & 0.04 & 0.04 & 0.97 \\ 
   \hline
\end{tabular}
\end{center}
\caption{log time taken}

\end{table}

### 2012-03-29 experiment.tex
working on intro, added/fixed references
second experiment

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3in]{turk4_samplesize_correctn.pdf}  
   \caption{For each sample size for polar and Euclidian coordinates, the bars are colored according to the number of correct responses. Darker colors indicate lower accuracy levels while lighter colors indicate higher accuracy levels. }
   \label{samp_size_acc}
\end{figure}

@@

The effect of a reference line on accuracy and time was not significant for both types of charts.

>>>>

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   %\includegraphics[width=3in]{turk4_samplesize_correctn.pdf}  
   \caption{For each sample size for polar and Euclidian coordinates, the bars are colored according to the number of correct responses. Darker colors indicate lower accuracy levels while lighter colors indicate higher accuracy levels. }
   \label{samp_size_acc}
\end{figure}

@@

The effect of a reference line on accuracy and time was not statistically significant for both types of charts. When looking at plots of the data, however, the time spent on the charts seems to be higher when there is a reference line.This is true for both Euclidian and polar charts. Also visible in the data is a slight increase in accuracy with the presence of a reference line. These characteristics can be seen in figure\ref{reflines}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2in]{turk4_refilne_time.pdf}  
   \includegraphics[width=2in]{turk4_refline_correctn.pdf}  
   \caption{The relationship between reference line and time spent (left) and the relationship between reference line and accuracy (right). Although not statistically significant, some patterns are visible.}
   \label{reflines}
\end{figure}

### 2012-03-29 setup.tex
second experiment

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
\rowcolors{2}{white}{lightgray}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std..Error & t.value & pval \\ 
  \hline
(Intercept) & 3.58 & 0.09 & 41.34 & 0.00 \\ 
  test\_parampolar & 0.22 & 0.10 & 2.17 & 0.03 \\ 
  reflineTRUE & 0.08 & 0.06 & 1.50 & 0.13 \\ 
  sample\_size & -0.03 & 0.00 & -8.73 & 0.00 \\ 
  offset90 & -0.06 & 0.08 & -0.72 & 0.47 \\ 
  offset180 & 0.16 & 0.08 & 2.07 & 0.04 \\ 
  offset270 & -0.04 & 0.07 & -0.54 & 0.59 \\ 
  test\_parampolar:reflineTRUE & -0.03 & 0.08 & -0.40 & 0.69 \\ 
  test\_parampolar:sample\_size & 0.03 & 0.01 & 6.25 & 0.00 \\ 
  test\_parampolar:offset90 & 0.14 & 0.11 & 1.23 & 0.22 \\ 
  test\_parampolar:offset180 & -0.17 & 0.11 & -1.55 & 0.12 \\ 
  test\_parampolar:offset270 & 0.17 & 0.11 & 1.50 & 0.13 \\ 
   \hline
\end{tabular}}
\end{center}
\caption{\label{tbl:time} Model output for (log) time taken. }
\end{table}

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
\rowcolors{2}{white}{lightgray}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std..Error & t.value & pval \\ 
  \hline
(Intercept) & 2.92 & 0.16 & 18.17 & 0.00 \\ 
  test\_parampolar & -0.30 & 0.16 & -1.86 & 0.06 \\ 
  reflineTRUE & -0.16 & 0.09 & -1.74 & 0.08 \\ 
  sample\_size & 0.01 & 0.01 & 1.01 & 0.31 \\ 
  offset90 & 0.14 & 0.13 & 1.07 & 0.28 \\ 
  offset180 & 0.03 & 0.13 & 0.26 & 0.80 \\ 
  offset270 & 0.01 & 0.12 & 0.07 & 0.94 \\ 
  test\_parampolar:reflineTRUE & 0.31 & 0.13 & 2.46 & 0.01 \\ 
  test\_parampolar:sample\_size & -0.01 & 0.01 & -0.70 & 0.49 \\ 
  test\_parampolar:offset90 & -0.14 & 0.18 & -0.78 & 0.44 \\ 
  test\_parampolar:offset180 & -0.01 & 0.18 & -0.04 & 0.97 \\ 
  test\_parampolar:offset270 & -0.00 & 0.18 & -0.01 & 0.99 \\ 
   \hline
\end{tabular}
}
\end{center}
\caption{\label{tbl:confidence} Model output for confidence level. }
\end{table}

>>>>

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
\rowcolors{2}{white}{lightgray}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std..Error & t.value & pval \\ 
  \hline
(Intercept) & 3.58 & 0.09 & 41.34 & 0.00 \\ 
  polar & 0.22 & 0.10 & 2.17 & 0.03 \\ 
  reflineTRUE & 0.08 & 0.06 & 1.50 & 0.13 \\ 
  sample\_size & -0.03 & 0.00 & -8.73 & 0.00 \\ 
  offset90 & -0.06 & 0.08 & -0.72 & 0.47 \\ 
  offset180 & 0.16 & 0.08 & 2.07 & 0.04 \\ 
  offset270 & -0.04 & 0.07 & -0.54 & 0.59 \\ 
  polar:reflineTRUE & -0.03 & 0.08 & -0.40 & 0.69 \\ 
  polar:sample\_size & 0.03 & 0.01 & 6.25 & 0.00 \\ 
  polar:offset90 & 0.14 & 0.11 & 1.23 & 0.22 \\ 
  polar:offset180 & -0.17 & 0.11 & -1.55 & 0.12 \\ 
  polar:offset270 & 0.17 & 0.11 & 1.50 & 0.13 \\ 
   \hline
\end{tabular}}
\end{center}
\caption{\label{tbl:time} Model output for (log) time taken. }
\end{table}

\begin{table}[ht]
\begin{center}
%\resizebox{\linewidth}{!} {
\rowcolors{2}{white}{lightgray}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std..Error & t.value & pval \\ 
  \hline
(Intercept) & 2.92 & 0.16 & 18.17 & 0.00 \\ 
  polar & -0.30 & 0.16 & -1.86 & 0.06 \\ 
  reflineTRUE & -0.16 & 0.09 & -1.74 & 0.08 \\ 
  sample\_size & 0.01 & 0.01 & 1.01 & 0.31 \\ 
  offset90 & 0.14 & 0.13 & 1.07 & 0.28 \\ 
  offset180 & 0.03 & 0.13 & 0.26 & 0.80 \\ 
  offset270 & 0.01 & 0.12 & 0.07 & 0.94 \\ 
  polar:reflineTRUE & 0.31 & 0.13 & 2.46 & 0.01 \\ 
  polar:sample\_size & -0.01 & 0.01 & -0.70 & 0.49 \\ 
  polar:offset90 & -0.14 & 0.18 & -0.78 & 0.44 \\ 
  polar:offset180 & -0.01 & 0.18 & -0.04 & 0.97 \\ 
  polar:offset270 & -0.00 & 0.18 & -0.01 & 0.99 \\ 
   \hline
\end{tabular}
%}
\end{center}
\caption{\label{tbl:confidence} Model output for confidence level. }
\end{table}
